Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-08-13 Scripts/Initial_Analysis.Rmd
misc changes

@@

# Load all sp in one table
Eme_Res <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  ) %>% 
  left_join(Neighbours,
            by = c("eez_name","eez_neighbour"))
# warnings() for empty data species

@@

# Load it!
World_eez_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 100)

@@

data %>% 
  left_join(data_eez,
            by = "emerging_yr") %>% 
  ggplot() +
  geom_point(
    aes(
      x = emerging_eez,
      y = emerging_tax,
      fill = emerging_yr,
      colour = emerging_yr
    )
  )

@@

data %>% 
  left_join(data_eez,
            by = "emerging_yr") %>% 
  rename(year = emerging_yr) %>% 
  left_join(sst_data) %>% 
  ggplot() +
  geom_point(
    aes(
      x = mean_temp,
      y = emerging_eez,
      fill = year,
      colour = year
    )
  )

@@

map <- World_eez_sf %>% 
  left_join(eez_d_hist,
            by = "eez_name") %>% 
  # filter(Tresh == "Tresh_one") %>%
  ggplot() +
  geom_sf(
    aes(
      fill = mean_yr
    )
  ) +
  geom_sf(data =World_map, aes(), size = 0.1, fill = "gray90", col = "gray90") +
  scale_fill_viridis() +
  my_ggtheme_m() +
  facet_wrap(~Tresh,
             ncol = 1) +
  ggsave("./Figures/emer_map_T12.png",
         width = 12,
         height = 10,
         units = "in"
  )

>>>>

```{r Emergence-analysis, eval = F, echo =F}

@@

# Load all sp in one table
Eme_Res <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  ) %>% 
  left_join(Neighbours,
            by = c("eez_name","eez_neighbour")
            )
# warnings() for empty data species

@@

# Load it!
World_eez_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=eck4") %>% 
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1)

@@

data_stock %>% 
  left_join(data_eez,
            by = "emerging_yr") %>% 
  ggplot() +
  geom_point(
    aes(
      x = emerging_eez,
      y = emerging_tax,
      fill = emerging_yr,
      colour = emerging_yr
    )
  )

@@

data_stock %>% 
  left_join(data_eez,
            by = "emerging_yr") %>% 
  rename(year = emerging_yr) %>% 
  left_join(sst_data) %>% 
  ggplot() +
  geom_point(
    aes(
      x = mean_temp,
      y = emerging_eez,
      fill = year,
      colour = year
    )
  )

@@

map <- World_eez_sf %>% 
  left_join(eez_d_hist,
            by = "eez_name") %>% 
  filter(Tresh == "Tresh_two",
         metric == "mean_yr") %>%
  ggplot() +
  geom_sf(
    aes(
      fill = value
    )
  ) +
  geom_sf(data =World_map, aes(), size = 0.1, fill = "gray90", col = "gray90") +
  scale_fill_viridis() +
  my_ggtheme_m() +
  # facet_wrap(~Tresh,
             # ncol = 1) +
  ggsave("./Figures/emer_map_T2a.png",
         width = 12,
         height = 10,
         units = "in"
  )
